---
title: "Survey Data Investigation"
author: "Eliza"
date: "5/14/2019"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    df_print: paged
---

## Conclusion
Cause of duplicates:

- going back to previous day/pages (already disabled)
- submit, then refresh → form submitted again upon refreshing

Cause of missing values:

- submit, refresh  → skip next page without filling
- while duplicating previous page's answers

All of the above would be solved after implementing "validation"

- users will not be able to skip page by refreshing
- no more missing/duplication

## Purpose
To investigate the cases where there is:  

- duplicated survey answers or 
- missing survey answers

```{r setup, include=TRUE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr) 
library(tidyverse)
```

## Data
### 1. Import data
```{r import}
all_results <- read.csv("allResults.csv", header = F, sep = ",")
names(all_results) <- c("user_id", "day", "question", "answer", "timestamp")

head(all_results)
```

### 2. Clean up
Tidy up user_id:

- User ID mapping from old to new convention
- Remove irrelevant users
```{r clean}
print("previous user_ids")
all_users <- all_results$user_id %>% unique()
all_users

# remove user 1 to 5
all_results <- all_results %>% filter(all_results$user_id > 5)

# rename to new user_id
all_results$user_id[all_results$user_id == 112] <- 2884055
all_results$user_id[all_results$user_id == 111] <- 3780005
all_results$user_id[all_results$user_id == 110] <- 4125240
all_results$user_id[all_results$user_id == 109] <- 5338852
all_results$user_id[all_results$user_id == 108] <- 6467910
all_results$user_id[all_results$user_id == 107] <- 8194629
all_results$user_id[all_results$user_id == 106] <- 9331127
all_results$user_id[all_results$user_id == 105] <- 10960925
all_results$user_id[all_results$user_id == 104] <- 11459752 

print("updated user_ids")
all_users_updated <- all_results$user_id %>% unique()
all_users_updated
```

## Duplicates
### 3. Get duplicates
Count number of entries by day, extract duplicates
```{r count}
# more than one entry 
duplicates <- all_results %>% 
  select(user_id, day, question) %>%
  group_by_all() %>% 
  summarise(count = n()) %>% 
  filter(count > 1)

duplicates <- merge(duplicates, all_results)
number_of_dup <- nrow(duplicates)
cat("Total number of duplicates:", number_of_dup)
```

### 4. Analyze duplicates
```{r duplicates}
# remove expected duplicates

# day 6 recallWhichAirQualitySource 
duplicates <- duplicates %>% filter(!(day==6 & question=="recallWhichAirQualitySource"))

# day 7 whoToldMe 
duplicates <- duplicates %>% filter(!(day==7 & question=="whoToldMe"))

# user 1882385 (Eliza testing)
duplicates <- duplicates %>% filter(!(user_id==1882385))

duplicates <- duplicates %>% 
  arrange(day, user_id)
  
duplicates
```

#### - Duplication case 1
```{r dup_case1}
# same day, same question, different answer
duplicates_diff_ans <- duplicates %>% slice(72:73)
duplicates_diff_ans
```

#### - Duplication case 2
```{r dup_case2}
# same day, same question, same answer
duplicates_same_ans <- duplicates %>% slice(24:25)
duplicates_same_ans
```

### 5. Hypothesis about duplicates
There are 2 categories of duplicates

- Duplication case 1: same day, same question, different answer
  - before "no access to previous surveys" was enfored (solved)
- Duplication case 2: same day, same question, same answer
  - refreshing page after submitting → multiple submissions
  - same timestamp to minutes, should be difference in seconds (see the test below with current result data)

### 6. Test hypothesis about duplicates
Test hypothesis with more detailed timestamps
```{r time}
# allResultsTime.csv contains more detailed timestamps (after changing templates)
all_results_time <- read.csv("allResultsTime.csv", header = F, sep = ",")
names(all_results_time) <- c("user_id", "day", "question", "answer", "timestamp")

# remove user 1 to 5
all_results_time <- all_results_time %>% filter(all_results_time$user_id > 5)

# more than one entry 
duplicates_time <- all_results_time %>% 
  select(user_id, day, question) %>%
  group_by_all() %>% 
  summarise(count = n()) %>% 
  filter(count > 1)

duplicates_time <- merge(duplicates_time, all_results_time)

# remove expected duplicates

# day 6 recallWhichAirQualitySource 
duplicates_time <- duplicates_time %>% filter(!(day==6 & question=="recallWhichAirQualitySource"))

# day 7 whoToldMe 
duplicates_time <- duplicates_time %>% filter(!(day==7 & question=="whoToldMe"))

# user 1882385 (Eliza testing)
duplicates_time <- duplicates_time %>% filter(!(user_id==1882385))

duplicates_time <- duplicates_time %>% 
  arrange(day, user_id)

duplicates_time
```

#### - Duplication case 1
```{r dup_time_case1}
# same day, same question, different answer, different time-stamp (to seconds)
print("Does not exist: no access to previous survey.")
```

#### - Duplication case 2
```{r dup_time_case2}
# same day, same question, same answer, different time-stamp (to seconds)
duplicates_time_same_ans <- duplicates %>% slice(43:48)
duplicates_time_same_ans
```

### 7. Demo for duplicates
Steps:  
1. Run flask locally, post user 1 activity to day 1  
2. Refresh after submitting user 1 day 1 page 1  

Results (<span style="color:green">submit time</span>, <span style="color:red">refresh time</span>):  

- allResults:  
  1,1,eventName,option2,2019-05-15 <span style="color:green">04:41:20.550263</span>  
  1,1,signUpFee,50,2019-05-15 <span style="color:green">04:41:20.550263</span>  
  1,1,eventName,option2,2019-05-15 <span style="color:red">04:41:38.888190</span>  
  1,1,signUpFee,50,2019-05-15 <span style="color:red">04:41:38.888190</span>  
  
- allActivities:  
  1,1,0,2,2019-05-15 04:40:47.719237,2019-05-15 <span style="color:red">04:41:38.888190</span>      
  
## Missing Answers
### 8. What are missing?
```{r}
# remove irrelevant (answer, time, duplicates), sort by user_id and day
all_results_simplified <- all_results %>% 
  select(user_id, day, question) %>% 
  unique() %>% 
  arrange(user_id, day)

# remove none compulsory questions
day1_optional <- c("dontKnowFamilyFriends", "dontKnowStrangers", "dontKnowForeigners", "dontKnowMedia", "dontKnowGovernment", "dontKnowHS", "dontKnowNGO","dontKnowCorporation")
day2_optional <- c("dontKnowPeoplesDaily", "dontKnowMorningPost", "dontKnowFM", "dontKnowSEMC", "dontKnowCNTA", "dontKnowNYT", "otherUniAnswer", "otherMailInfo", "dormName", "roomNum")
day3_optional <- c("activity2", "activity3")
day6_optional <- c("walkathonSteps", "otherSourceNumberOfTimes", "otherWeatherSource", "weatherNumberOfTimes", "weatherInfoFrom", "dontKnowPeoplesDaily", "dontKnowMorningPost", "dontKnowFM", "dontKnowSEMC", "dontKnowCNTA", "dontKnowNYT")
day7_optional <- c("walkathonSteps")
  
all_results_simplified <- all_results_simplified %>% 
  filter(!question %in% c(day1_optional, day2_optional, day3_optional, day6_optional, day7_optional)) 
  
# count number of questions by day for each user
count_qn_no <- all_results_simplified %>% 
  arrange(user_id, day) %>% 
  group_by(user_id, day) %>% 
  count() %>% 
  spread(key = day, value = n)
names(count_qn_no) <- c("user_id", "d0", "d1", "d2", "d3", "d4", "d5", "d6", "d7")
count_qn_no

# count no. of compulsory questions based on survey
#                            2   3   4   5   6   7   8   9
#                           d0  d1  d2  d3  d4  d5  d6  d7
required <- list("required", 1, 22, 26, 11, 1,  1,  21, 14)

get_missing <- function(curr_user_id, curr_all_day, curr_day) {
  curr_answers_day <- all_results_simplified %>% 
    filter(user_id == curr_user_id & day == curr_day) %>% 
    select(question)
  curr_missing_ans <- setdiff(curr_all_day, curr_answers_day)
  return(curr_missing_ans)
}
```

#### - Day 1 missing answers
```{r missing_d1}
missing_d1 <- count_qn_no %>% filter(d1 < 22) 
missing_d1
all_d1 <- all_results_simplified %>% 
  filter(user_id == 1882385 & day == 1) %>% 
  select(question)

get_missing(21853588, all_d1, 1)
get_missing(23300203, all_d1, 1)
get_missing(25097422, all_d1, 1)
```

#### - Day 2 missing answers
```{r missing_d2}
missing_d2 <- count_qn_no %>% filter(d2 < 26) 
missing_d2
all_d2 <- all_results_simplified %>% 
  filter(user_id == 1882385 & day == 2) %>% 
  select(question)

# get_missing(2884055, all_d2, 2)
# get_missing(13330179, all_d2, 2)
get_missing(16067600, all_d2, 2)
```

#### - Day 3 missing answers
```{r missing_d3}
missing_d3 <- count_qn_no %>% filter(d3 < 11) 
missing_d3
all_d3 <- all_results_simplified %>% 
  filter(user_id == 1882385 & day == 3) %>% 
  select(question)

get_missing(9331127, all_d3, 3)
```

#### - Day 6 missing answers
```{r missing_d6}
missing_d6 <- count_qn_no %>% filter(d6 < 21)
missing_d6
all_d6 <- all_results_simplified %>% 
  filter(user_id == 1882385 & day == 6) %>% 
  select(question)

get_missing(8194629, all_d6, 6)
get_missing(15312225, all_d6, 6)
# get_missing(19949432, all_d6, 6)
```

#### - Day 7 missing answers
```{r missing_d7}
missing_d7 <- count_qn_no %>% filter(d7 < 14)
missing_d7
all_d7 <- all_results_simplified %>% 
  filter(user_id == 3780005 & day == 7) %>% 
  select(question)

get_missing(8194629, all_d7, 7)
get_missing(14276185, all_d7, 7)
get_missing(17737049, all_d7, 7)
get_missing(22535066, all_d7, 7)
```

### 9. Hypothesis about missing answers
Relationship between missing value and duplicates:

- except for those who did not finish (in missing), all missing have corresponding duplicates
- suspect submit this page, then refresh → proceed to the next page → missing next page's answers, duplicate this page's answers
```{r dup_and_missing}
all_dup_user_id_day <- duplicates %>% 
  select(user_id, day) %>% 
  unique()
all_dup_user_id_day

missing_d1$day <- 1
missing_d2$day <- 2
missing_d3$day <- 3
missing_d6$day <- 6
missing_d7$day <- 7
all_missing_user_id_day <- bind_rows(missing_d1, missing_d2, missing_d3, missing_d6, missing_d7) %>% 
  select(user_id, day)
all_missing_user_id_day

overlap <- merge(all_dup_user_id_day, all_missing_user_id_day)
overlap
```

### 10. Demo for missing answers
Steps:  
1. Run flask locally, post user 1 activity to day 1    
2. Refresh after submitting user 1 day 1 page 1   
3. Proceed to next page without filling current page  

Results:  

- allResults:   
  1,1,eventName,option1,2019-05-15 09:16:18.034667  
  1,1,signUpFee,120,2019-05-15 09:16:18.034667  
  1,1,eventName,option1,2019-05-15 09:16:25.727473  
  1,1,signUpFee,120,2019-05-15 09:16:25.727473  
  1,1,eventName,option1,2019-05-15 09:16:29.792935  
  1,1,signUpFee,120,2019-05-15 09:16:29.792935  
  1,1,eventName,option1,2019-05-15 09:16:55.957516  
  1,1,signUpFee,120,2019-05-15 09:16:55.957516  
  1,1,eventName,option1,2019-05-15 09:16:59.561099  
  1,1,signUpFee,120,2019-05-15 09:16:59.561099    
  
- allActivities:  
  1,<span style="color:red">1,1,5</span>,2019-05-15 09:16:05.116206,2019-05-15 09:16:59.561099      
[End]